# Method
```{r}
compute_new = FALSE

source("prep_data.R")

if (compute_new) source("prepare_results.R")

source("results_paper.R")
```

In order to collect evidence from as many datasets as possible, we retrieved data from the Truth Effect Database (TED) [@lescheIntroducingTruthEffect2026], an open database for research focusing on the illusory truth effect (ITE). 
<!-- In total, we extracted data from `r n_publications_original` publications, contributing `r n_studies_original` studies, `r n_participants_original` participants, and a total of `r n_trials_original` trials. -->
We only included data from the judgment phase, excluded missing data in either the response or the repetition status and excluded studies where the ITE was measured between-participants and studies where the response format allowed a "neutral" response. We therefore excluded all studies with sliders and studies using likert scale ratings with an odd number of response options.

```{r}
study_overview <- study_overview %>% 
  filter(study_id %in% unique(analysis_data$study_id)) 

age_data <- study_overview %>% 
  mutate(participant_age = ifelse(participant_age == 99, NA, participant_age)) %>% 
  filter(!is.na(participant_age), !is.na(n_participants))

n_dichotomous <- sum(study_overview$truth_rating_scale == "dichotomous")
n_likert <- sum(study_overview$truth_rating_scale == "likert")
n_range <- sum(study_overview$truth_rating_scale == "range")
n_scale <- n_likert + n_range

```

Of the `r length(unique(analysis_data$study_id)) %>% apa_num()` remaining studies following exclusion, `r n_dichotomous` employed a dichotomous response format to truth judgments, whereas `r n_scale` studies employed a scale response format.

The number of participants ranged from `r min(study_overview$n_participants, na.rm = TRUE)` to `r max(study_overview$n_participants, na.rm = TRUE)`. On average, studies included `r mean(study_overview$n_participants, na.rm = TRUE)` participants ($\mu_{age} =$ `r weighted.mean(age_data$participant_age, age_data$n_participants, na.rm = TRUE)`,$\sigma_{age} =$ `r DescTools::SD(age_data$participant_age, weights = age_data$n_participants, na.rm = TRUE)`). 

## Analysis
The ITE was operationalized as the within-participant difference in truth judgments between repeated and new statements. All truth and certainty ratings were maximum-normalized to the [0, 1] interval prior to analysis.

Effect sizes (Cohen's d for paired samples) were computed from participant-level mean truth judgments for repeated and new items. Reliability was estimated using split-half correlations, corrected with the Spearman–Brown formula as implemented in the splithalf package (@R-splithalf). Trials were randomly split within participants and conditions, and the procedure was repeated 5,000 times, with estimates averaged across iterations.

To examine the impact of response format, we generated counterfactual datasets. Likert responses were pseudo-dichotomized at the scale midpoint, and pseudo-certainty was derived from the distance to the midpoint. Conversely, in datasets containing separate certainty ratings, dichotomous truth judgments were transformed into continuous responses by combining judgment direction with certainty and rescaling the resulting values to the [0, 1] interval.

Average effect sizes and reliabilities across original and counterfactual datasets were analyzed using multilevel random-effects meta-analysis. Models included response format (dichotomous vs. scale), condition (original vs. counterfactual), and their interaction as fixed effects, with random intercepts for experiments (procedure_id) to account for non-independence of estimates. Sampling variances were approximated from confidence intervals.

## Transparency and Openness
We did not predetermine sample size. All data, analysis code, and research materials are available at https://doi.org/10.5281/zenodo.20796312. All analysis were conducted using `r r_cite_intext`. Additional information on packages is available in the appendix.